---
title: "Electric_vs_Gas_comparison"
author: "Javier Patron"
date: "2022-08-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

### In this Markdown document we will create a model on rental cars prices so you can select the best option regarding price and carbon offset

### Electric Car Price

Variables: Total Days, Rental Cost (per day), Total Distance planned , Fully Charge Cost, Range (miles)

```{r}

tot_e_cost <- function(tot_days, rent_cost, dist_plan, full_battery_cost, range) {
  tot_e_cost = tot_days * rent_cost + (dist_plan * full_battery_cost)/range
  print(tot_e_cost)
}



```

## Test e-car

Total Days: 3

Rental Car price (per day): \$60

Total trip distance planned (miles): 105.5 \* 2

Cost to charge a full battery Cost (dlls) : \$18.29

Range (miles): Tesla Model S: 405 miles

```{r}
e_cost <- tot_e_cost(tot_days = 3, rent_cost = 60, dist_plan = 105.5, full_battery_cost = 18.29, range = 405)

```

### Fuel Car Price

Variables: Total Days, Rental Cost (per day), Total Distance planned , Full Tank Cost, Range (miles)

```{r}
tot_fuel_cost <- function(tot_days, rent_cost, dist_plan, full_tank_cost, range) {
  tot_fuel_cost = tot_days * rent_cost + (dist_plan * full_tank_cost)/range
  print(tot_fuel_cost)
        
}
```

## Test fueled car

Total days: 3

Rental car price (per day): \$40

Total trip distance planned (miles): 105.5 \* 2

Cost fill the tank (dlls) : \$51.50

Range (miles): Honda Civic : 446 miles

```{r}
fuel_cost <- tot_fuel_cost(tot_days = 3, rent_cost = 40, dist_plan = 105.5*2, full_tank_cost = 51.50, range = 446)
```

## Lets make a data.frame with different distances

Vectors with the Electric Vehicle Day 1, Different distances

```{r}

e_day_1 <- tot_e_cost(1,60,seq(from=80, to=2000, by=80), 18.29, 405)
e_day_2 <- tot_e_cost(2,60,seq(from=80, to=2000, by=80), 18.29, 405)
e_day_3 <- tot_e_cost(3,60,seq(from=80, to=2000, by=80), 18.29, 405)
e_day_4 <- tot_e_cost(4,60,seq(from=80, to=2000, by=80), 18.29, 405)
e_day_5 <- tot_e_cost(5,60,seq(from=80, to=2000, by=80), 18.29, 405)
```

Vectors with the Fuel Vehicle Day 1, Different distances

```{r}
fuel_day_1 <- tot_fuel_cost(1, 40, seq(from=80, to=2000, by = 80), 51.50, 446)
fuel_day_2 <- tot_fuel_cost(2, 40, seq(from=80, to=2000, by = 80), 51.50, 446)
fuel_day_3 <- tot_fuel_cost(3, 40, seq(from=80, to=2000, by = 80), 51.50, 446)
fuel_day_4 <- tot_fuel_cost(4, 40, seq(from=80, to=2000, by = 80), 51.50, 446)
fuel_day_5 <- tot_fuel_cost(5, 40, seq(from=80, to=2000, by = 80), 51.50, 446)
```

Create the Data Frame

```{r}
comp_1_df <- data.frame(distance = seq(80,2000,80),e1 = e_day_1, f1 = fuel_day_1, e2 = e_day_2, f2 = fuel_day_2, f3 = fuel_day_3, e3 = e_day_3, e4 = e_day_4, f4 = fuel_day_4, e5 = e_day_5, f5 = fuel_day_5)
```

Graph

ggplot(economics, aes(x=date)) + geom_line(aes(y = psavert), color = "darkred") + geom_line(aes(y = uempmed), color="steelblue",

```{r}
ggplot(comp_1_df, aes(x=distance))+
  geom_line(aes(y= e1), color = "red") +
  geom_line(aes(y= f1), color = "darkred") +
  geom_line(aes(y= e2), color = "blue", linetype = "twodash") +
  geom_line(aes(y= f2), color = "darkblue", linetype = "twodash") +
  geom_line(aes(y= e3), color = "green", linetype = "longdash") +
  geom_line(aes(y= f3), color = "darkgreen", linetype = "longdash") +
  geom_line(aes(y= e4), color = "orange", linetype = "dotdash") +
  geom_line(aes(y= f4), color = "darkorange", linetype = "dotdash") +
  geom_line(aes(y= e5), color = "gray", linetype = "dashed") +
  geom_line(aes(y= f5), color = "darkgray", linetype = "dashed") +
  labs(title = "Electric vs. Fuel Rental Vehicles", x = "Distance(Miles)", y= "Total Cost (dls $)") + 
  scale_color_manual(name = "lines")
```

### Find the intersection point between the lines on the same days

```{r}

#EQUIATION FOR E1
# y = mx + b
# m = (y2 -y1) / (x2 - x1)

# Calculate m
m_e5 <- (comp_1_df$e5[[2]]-comp_1_df$e5[[1]]) / (comp_1_df$distance[[2]]- comp_1_df$distance[[1]] )
m_e5

# Calculate b of point 1 (80, 64.5)
b_e5 <- comp_1_df$e5[[1]] - (m_e1 * comp_1_df$distance[[1]]) 
b_e5

```

Testing M for electric car

```{r}
b_electric <- ((1 * 60) + (0 * 18.29)/405) - (0.04516049 * ((1 * 60) + (0 * 18.29)/405))

b_electric
```

```{r}

#EQUIATION FOR F1
# y = mx + b
# m = (y2 -y1) / (x2 - 11)

# Calculate m
m_f1 <- (comp_1_df$f1[[2]]-comp_1_df$f1[[1]]) / (comp_1_df$distance[[2]]- comp_1_df$distance[[1]])
m_f1

# Calculate b of point 2 (80, 51.54)
b_f1 <- comp_1_df$f1[[1]] - (m_f1 * comp_1_df$distance[[1]]) 
b_f1
```

Create a function to get X value for the intersection point

```{r}

#Electric line
# e1 equation: y = m_e1 * x + b_e1
# system equation = -m_e1 * x + y = b_e1

#Fuel line
# f1 equation: y = m_f1 * x + b_f1
# system equation = -m_f1 * x + y = b_f1


A <- rbind(c(-m_e1, 1), c(-m_f1, 1))
B <- c(60, 40)

solve(A,B)

```

```{r}
# Question: how can you extrapolate a line given by points to infinate limits ??
ggplot(data = comp_1_df, aes(x = distance)) + 
  geom_line(aes(y=e1)) +
  xlim(-10,10) + 
  ylim(-10,100)
```

# Testing function price delta

## Electric car specs:

Total Days: 3

Rental Car price (per day): \$60

Total trip distance planned (miles): 105.5 \* 2

Cost to charge a full battery Cost (dlls) : \$18.29

Range (miles): Tesla Model S: 405 miles

## Fuel car specs

Total days: 3

Rental car price (per day): \$40

Total trip distance planned (miles): 105.5 \* 2

Cost fill the tank (dlls) : \$51.50

Range (miles): Honda Civic : 446 miles

```{r}
price_delta(3, 60, 105.5*2, 18.29,405,40,51.50,446)
```

```{r}
slope_fuel <- (((1 * 40) + ((10000 * 51.50)/446)) - ((1 * 40) + (0 * 51.50)/446)) / 10000
```

```{r}
A <- rbind(c(-m_e1, 1), c(-slope_fuel, 1))
B <- c(100,40)

results <- solve(A,B)

results[1]
```

```{r}

price_delta(1,100,1000,18.29,405,40,51.50,446)

```
